The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-08-14 script/en/chapters/what-is-sage.tex
CT script: Sage parts finished in (en); translation to German almost finished

% ---------------------------------------------------------------------------
\newpage
\hypertarget{appendix-using-sage}{}
\section{Using Sage with this Script}
\label{s:appendix-using-sage}
\index{Sage}

This script includes numerous code samples using Sage. Sage is an open
source computer algebra system (CAS) that supports teaching, study and
research in mathematics.  It combines many high-quality open
source packages\footnote{%
To get an impression, how big Sage is: After downloading the source of Sage 4.1,
it took around 5 h on a average Linux PC to compile the whole system including
all libraries, and it occupied 1.8 GB disk space.
% ist jetzt fertig übersetzt.
%Ich nach noch kash3-2008-07-31.spkg nachinstalliert, dieses Paket wird für Frau Massierers ECC Notebooks benötigt.
%Das Übersetzen hat fast 5 Stunden gebraucht. Sage 4.1 belegt 1,8GB.
}
and provides access to their functionalities via a
common interface, namely, a Python\footnote{%
There is also an easy interface to the C language, called Cython, which can be used
to speed up own functions in Sage very much.\\
See \url{http://openwetware.org/wiki/Open_writing_projects/Sage_and_cython_a_brief_introduction}.
} based programming language.

@@

%% \centering statt \begin{center} ... \end{center}, da dies zusätzlich vertical space erzeugt.
\noindent There are lots of PDF or HTML documents about using Sage,
so we name only a few of them: A good starting point is the ``Library''
from the Sage main page, the ``Documentation Project'' and the teaching
material\footnote{%
- ``Library'': {\centering \url{http://www.sagemath.org/library/index.html}},\\
- ``Documentation Project'': {\centering \url{http://wiki.sagemath.org/DocumentationProject}},\\
- ``Teaching'': {\centering \url{http://wiki.sagemath.org/Teaching_with_SAGE}}.
}.

@@

# * Finite Fields:
    sage: F.<x>=GF(2)[]
    sage: G.<a>=GF(2^4,name='a',modulus=x^4+x+1)
    sage: a^2/(a^2+1)
      a^3 + a
    sage: a^100
      a^2 + a + 1
    sage: log(a^2,a^3+1)
      13
    sage: (a^3+1)^13
      a^2
\end{Verbatim}
\caption{Some small general samples from different araes in mathematics}
\end{sagecode}

@@

>>>>

% ---------------------------------------------------------------------------
\newpage
\hypertarget{appendix-using-sage}{}
\section{Using Sage with this Script}
\label{s:appendix-using-sage}
\index{Sage}
\index{Sage!Code examples}

This script includes numerous code samples using Sage. Sage is an open
source computer algebra system (CAS) that supports teaching, study and
research in mathematics.  It combines many high-quality open
source packages\footnote{%
To get an impression, how big Sage is: After downloading the source of Sage 4.1,
it took around 5 h on a average Linux PC to compile the whole system including
all libraries, and it occupied 1.8 GB disk space then.
}
and provides access to their functionalities via a
common interface, namely, a Python\footnote{%
There is also an easy interface to the C language, called Cython, which can be used
to speed up own functions in Sage very much.\\
See \url{http://openwetware.org/wiki/Open_writing_projects/Sage_and_cython_a_brief_introduction}.
} based programming language.

@@

%% \centering statt \begin{center} ... \end{center}, da dies zusätzlich vertical space erzeugt.
\noindent In the meantime there are lots of PDF or HTML documents about using Sage,
so we name only a few of them: A good starting point is the ``Library''
from the Sage main page, the ``Documentation Project'' and the teaching
material\footnote{%
- ``Library'': {\centering \url{http://www.sagemath.org/library/index.html}},\\
- ``Documentation Project'': {\centering \url{http://wiki.sagemath.org/DocumentationProject}},\\
- ``Teaching'': {\centering \url{http://wiki.sagemath.org/Teaching_with_SAGE}}.
}.

@@

# * Finite Fields:
    sage: F.<x>=GF(2)[]
    sage: G.<a>=GF(2^4,name='a',modulus=x^4+x+1)
    sage: a^2/(a^2+1)
      a^3 + a
    sage: a^100
      a^2 + a + 1
    sage: log(a^2,a^3+1)
      13
    sage: (a^3+1)^13
      a^2
\end{Verbatim}
\caption{Some small general samples from different areas in mathematics}
\end{sagecode}

@@

\vspace{30pt}
To move quickly to the Sage code examples in this script, either look in the
index at \verb#Sage -> Code examples# or have a look at the
``\nameref{sc:List-of-Sage-Code-Examples}''.
